\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test for Goodness-of-Fit of Marginal Distributions of Stationary Time Series

### 2023-12-14 manuscript/manuscript.tex
Fixed Style Issues

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow the
hypothesized distribution~$F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}

@@

A common 
function for block size that is considered optimal is 
$l = \lceil n^{1/3} \rceil$, \citep{buhlmann1999block} 
which was adopted in this study.

@@

We constructed Q-Q plots of the distribution of the p-values to see if they are
uniformly distributed. If the distribution of the p-values is uniform, this 
indicates that under the null hypothesis, our method will only reject the $H_0$
at a rate of $\alpha$.
A zoomed in plot for probabilities between 0 and 0.1 is
also provided, as
that is the most common range for significance levels $\alpha$. 
%We can also
%compute the rate of rejection $\#P < \alpha$ for different values of
%$\alpha$, as well as a confidence interval
%for this proportion.

@@

Although the p-values do not appear to be completely aligned with the line
in the Q-Q plots for smaller sample sizes like $n = 100$ or $200$, they match
the lines very closely for $n = 1600$ and $3200$. More importantly, almost
all of the p-values appear to be within the confidence bands when looking at the
plots zoomed in to probabilities between 0 and 0.1, and as stated before, 
researchers are unlikely to choose significance levels above 0.1.

@@

Like we did to see if the test holds its size, we generated time series with marginal distributions $N(8, 8)$ and 
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is gamma, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is normal.
For each setting for $F$, $\phi$, and $n$, we replicate the method $R$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, R\}$.

@@

From Figure~\ref{table:rr_100}, we can see that when $n = 100$, the rejection rate may 
be quite low, especially for lower values of $\alpha$. From Figure~\ref{table:rr_200}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
from Figure~\ref{table:rr_400} that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

As shown in Figures~\ref{table:rr_800}, \ref{table:rr_1600}, and 
\ref{table:rr_3200}, the rejection rates for these settings are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

@@

\subsection{Precipitation in Mansfield Connecticut}
\label{sec:precipitation}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport (MDW), New York LaGuardia 
International 
Airport (LGA),
and Los Angeles International Airport (LAX) stations from the 
National Oceanic and Atmospheric Administration. These stations were selected 
from places of importance in the three largest American cities. LGA and
MDW were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data for MDW is from
1948 to 2014, the data for LGA is from 1948 to 2013, and the
data for LAX is also from 1948 to 2013. We can apply our method to
the precipitation time series from each of these locations to test if they
follow the
Generalized Extreme Value (GEV) distribution. Precipitation maximum series 
typically do follow the GEV distribution, so we expect to fail to reject the
null hypothesis.

@@

Using a significance level as high as .10 still results in a failed rejection
of the null hypothesis for each of the three tests that the respective 
time series follow the GEV distribution.

@@

We expect the marginal distribution of Microsoft stock returns to have a 
slightly
heavier tail than the normal distribution. Using the \textsl{tseries} package, 
\citet{tseries}
we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
Then we approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We can test that the stock returns are normally
distributed (which we expect to reject).  After that, we can test that the
marginal distribution of the time series follows the Student's $t$ distribution.
While we 
could choose to estimate a fitted value of the degrees of freedom parameter $v$
as
part of our method, it is very difficult to do so. Therefore, we can try testing 
if it follows
the $t$ distribution with increasingly smaller specified degrees of freedoms. We
can also observe how the method performs using increasingly smaller durations of
time. First, we try the entire data set which has a duration of 25 years. Then,
we use the last 5 years of data: January 1st, 2018 to December 31st, 2022.
Finally, we try the method only using the last year of data: January 1st, 2022
to December 31st, 2022.

@@

We observe that when the duration of time is large, our method rejects the null
hypothesis unless the degrees of freedom specified is very precise. When
we use 25 years of data, the method
only fails to reject the null hypothesis at $\alpha = .05$ when 
the hypothesized $v = 2.2$, when 
the precision
is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
hundredths place.
When using only 5 years of data, the method reaches a p-value of 
$0.05$ when the hypothesized $v = 2.5$, but the p-value is
lower for $v = 2.2$ and $v = 2.15$.
When we only use 1 year of data, the method fails to reject the null hypothesis
even when the hypothesized distribution family is normal ($v \to \infty$). The
p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
is lower for smaller values of $v$ when using only 1 year of data.

>>>>

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow the
hypothesized distribution~$F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}

@@

A common 
function for block size that is considered optimal is 
$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
which was adopted in this study.

@@

Using the \textsl{qqplotr} and \textsl{ggplot2} packages 
\citep{qqplotr, ggplot2},
we constructed Q-Q plots of the distribution of the p-values to see if they are
uniformly distributed. If the distribution of the p-values is uniform, this 
indicates that under the null hypothesis, our method will only reject the $H_0$
at a rate of $\alpha$.
A zoomed in plot for probabilities between 0 and 0.1 is
also provided, as
that is the most common range for significance levels $\alpha$. 
%We can also
%compute the rate of rejection $\#P < \alpha$ for different values of
%$\alpha$, as well as a confidence interval
%for this proportion.

@@

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the p-values do not appear to be 
completely aligned with the line
in the Q-Q plots for smaller sample sizes like $n = 100$ or $200$, they match
the lines very closely for $n = 1600$ and $3200$. More importantly, almost
all of the p-values appear to be within the confidence bands when looking at the
plots zoomed in to probabilities between 0 and 0.1 in 
Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}, and as stated 
before, 
researchers are unlikely to choose significance levels above 0.1.

@@

Like we did to see if the test holds its size, we generated time series with 
marginal distributions $N(8, 8)$ and 
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is gamma. Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0.
When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is normal.
For each setting for $F$, $\phi$, and $n$, we replicate the method $R$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, R\}$.

@@

From Table~\ref{table:rr_100}, we can see that when $n = 100$, the rejection 
rate may 
be quite low, especially for lower values of $\alpha$. From 
Table~\ref{table:rr_200}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
from Table~\ref{table:rr_400} that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

As shown in Tables~\ref{table:rr_800}, \ref{table:rr_1600}, and 
\ref{table:rr_3200}, the rejection rates for these settings are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

@@

\subsection{Precipitation in Mansfield Connecticut}
\label{sec:precipitation}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport (MDW), New York LaGuardia 
International 
Airport (LGA),
and Los Angeles International Airport (LAX) stations from the 
National Oceanic and Atmospheric Administration. These stations were selected 
from places of importance in the three largest American cities. LGA and
MDW were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data for MDW is from
1948 to 2014, the data for LGA is from 1948 to 2013, and the
data for LAX is also from 1948 to 2013. We can apply our method to
the precipitation time series from each of these locations to test if they
follow the
Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
package \citep{evd}. Precipitation maximum series 
typically do follow the GEV distribution, so we expect to fail to reject the
null hypothesis.

@@

As displayed in Table~\ref{table:precipitation}, using a significance level as 
high as .10 still results in a failed rejection
of the null hypothesis for each of the three tests that the respective 
time series follow the GEV distribution.

@@

We expect the marginal distribution of Microsoft stock returns to have a 
slightly
heavier tail than the normal distribution. Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
Then we approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed (which we expect to reject).  After that, we tested that the
marginal distribution of the time series follows the Student's $t$ distribution.
While we 
could choose to estimate a fitted value of the degrees of freedom parameter $v$
as
part of our method, it is very difficult to do so. Therefore, we attempted to
test 
if it follows
the location-scale $t$ distribution with increasingly smaller specified degrees 
of freedoms. This was achieved with the \textsl{extraDistr} 
package \citep{extraDistr}. We
also observed how the method performs using increasingly smaller durations of
time. First, we tred the entire data set which has a duration of 25 years. Then,
we used the last 5 years of data: January 1st, 2018 to December 31st, 2022.
Finally, we tried the method only using the last year of data: January 1st, 2022
to December 31st, 2022.

@@

The p-values of our test when applied to Microsoft stock return data using
different settings are showcased in Table~\ref{table:microsoft}.
We observe that when the duration of time is large, our method rejects the null
hypothesis unless the degrees of freedom specified is very precise. When
we use 25 years of data, the method
only fails to reject the null hypothesis at $\alpha = .05$ when 
the hypothesized $v = 2.2$, when 
the precision
is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
hundredths place.
When using only 5 years of data, the method reaches a p-value of 
$0.05$ when the hypothesized $v = 2.5$, but the p-value is
lower for $v = 2.2$ and $v = 2.15$.
When we only use 1 year of data, the method fails to reject the null hypothesis
even when the hypothesized distribution family is normal ($v \to \infty$). The
p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
is lower for smaller values of $v$ when using only 1 year of data.
